Haploid Selection, Sex Ratio Bias, and Transitions Between sex-determination systems

### 2017-08-16 LaTeX/Turnover.tex
new figures attempt

@@

@@

@@

@@

\newpage
\section*{Figures}
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
\caption{
In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
}
\label{fig:SexAntagTighter}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.45\linewidth]{regionplot_2a}
\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
\caption{
In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
Panel A shows the range of male homozygote fitnesses that allow both neo-W haplotypes to invade.
Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
}
\label{fig:BothOverdominance}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
\caption{
With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
}
\label{fig:LooseDecline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%A neo-W can invade an XY system under a large number of selective regimes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\linewidth]{PositionPlot_4}
\caption{
 A neo-W can invade an XY system under a large number of selective regimes.
In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.   
In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
}
\label{fig:Combination_Centimorgans}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Sex-ratio selection is not a good predictor of neo-W invasion into an XY system
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
\caption{
Sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
}
\label{fig:SexRatioBad}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Haploid selection can lead to polymorphic SD systems 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{Polymorphic}
\caption{
Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.   
}
\label{fig:Polymorphism}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%CYCLES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
\caption{
Thought I'd show this just for fun (not for publication).
}
\label{fig:Cycles}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

@@

With weak selection the leading eigenvalue, $\lambda$, for any $k$, is given up to order $\epsilon^2$ by equation \ref{eq:lambda_ESD_k}.
Scenarios leading to $\lambda>1$ are discussed in the main text.

@@

%\section*{Supplementary Figures}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_Mike}}
\caption{
Transitions between XY and ZW systems can occur even when the neo-SDR is more loosely linked to a locus under sexually-antagonistic selection (here, without haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$).
In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
In panel C we vary the recombination rate between the neo-W and the selected locus ($R$) for a fixed recombination rate between the ancestral-SDR and the selected locus ($r=0.005$). 
Coloured markers show recombination rates for which the temporal dynamics of invasion are plotted in the inset, demonstrating that neo-W alleles can fix (reach frequency $0.5$ among female gametes) if they are more (black) or less (red) closely linked to a locus experiencing sexually-antagonistic selection. 
A very loosely linked neo-W does not spread in this case (blue and green lines overlap and go to 0). 
Fitness parameters are shown by an asterisk in Figure \ref{fig:regionplots}: $w_{AA}^\female = 1.05$, $w_{aa}^\male = 1.2$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\Hermaphrodite = 1$.
}
\label{fig:SexAntagTighter}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=1.25\linewidth]{Region_plot_combined_Mike}}
\caption{
When the ancestral-XY locus is tightly linked to a locus under selection ($r=0$), one or both neo-W haplotypes can spread. 
We vary the fitness of male homozygotes relative to heterozygotes ($w_{Aa}^\Hermaphrodite=1$) and only consider stable equilibria at which the $a$ allele is initially fixed on the Y, as indicated. 
Here, selection in females can favour the $A$ allele (panel A, $w_{aa}^\female=0.85$, $w_{AA}^\female=1.05$), favour the $a$ allele (panel B, $w_{aa}^\female=1.05$, $w_{AA}^\female=0.85$), or be overdominant (panel C, $w_{aa}^\female=w_{AA}^\female=0.6$). 
If $\lambda_{wA}$ or $\lambda_{wa}$ is greater than one, then a rare neo-W can spread for, at least, some values of $R>r$. 
For the parameter values marked with an asterisk, example invasion dynamics are shown in Figure \ref{fig:SexAntagTighter}C. 
Where both $\lambda_{wA}$ and $\lambda_{wa}$ are greater than one, a neo-W will spread when rare, regardless of linkage with the selected locus (for any $R$). 
Figure \ref{fig:positionOverdominance} shows two examples using the parameters marked with a dagger. 
Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
}
\label{fig:regionplots}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%A neo-W can invade an XY system under a large number of selective regimes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\linewidth]{PositionPlot_4}
\caption{
 A neo-W can invade an XY system under a large number of selective regimes.
In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.   
In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
}
\label{fig:Combination_Centimorgans}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Sex-ratio selection is not a good predictor of neo-W invasion into an XY system
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{Temporal_SR_Mike}
\caption{
Fisherian sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
In this figure, selection is ploidally antagonistic with haploid selection favouring the $a$ allele during male meiosis ($s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$).
In panel A, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and replace the ancestral sex-determination system (see inset, the ancestral W also fixes). 
In this case, the neo-Y becomes associated with the allele favoured by drive, causing the zygotic sex ratio to become biased, hence the frequency of neo-Y among male gametes can be higher than $0.5$ (inset).
In panel B, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and replace the ancestral sex-determination system (see inset, the ancestral Y also fixes), which balances the sex ratio.
Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\male_\Delta = -0.2$, $r=0.02$.
}
\label{fig:SexRatioBad}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newpage
%\section*{Figures}
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Tighter linkage allows looser sex-linkage to evolve, even in absence of haploid selection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\includegraphics[width=\linewidth]{PositionPlot_SexAntagTighter}
%\caption{
%In the absence of haploid selection, tight linkage allows looser sex-linkage to evolve in transitions between XY and ZW systems.
%In panel A, linkage is loose enough relative to selection that the weak selection analytical results hold, and a neo-W can only invade when it is more tightly linked with the selected locus ($R<r$; shaded region).
%In panel B, linkage is tight enough relative to selection that the weak selection analytical results do no hold, and a neo-W can only invade even when it is less tightly linked with the selected locus ($r<R$; unshaded region).
%Parameters: $w_{AA}^\female = w_{aa}^\male = 1.05$, $w_{aa}^\female = w_{AA}^\male = 0.85$, $w_{Aa}^\female = 1$, $w_{Aa}^\male = 0.925$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
%}
%\label{fig:SexAntagTighter}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\includegraphics[width=0.45\linewidth]{regionplot_2a}
%\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
%\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
%\caption{
%In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
%Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
%The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
%The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
%The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
%Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
%Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
%Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
%\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
%}
%\label{fig:BothOverdominance}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%With weak selection, a less tightly linked neo-W can invade an XY system when there is some haploid selection, and this invasion decreases mean diploid fitness
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\includegraphics[width=0.5\linewidth]{Loose_Fitness_Decline}
%\caption{
%With weak selection, a less tightly linked neo-W can invade (and fix in) an XY system (causing the Y to fix in females) when there is some haploid selection (blue and green curves in panel A), and this invasion decreases mean diploid fitness (green and blue curves in panel B).
%Parameters: $s^\Hermaphrodite = 0.2$, $h^\Hermaphrodite = 0.7$, $t^\Hermaphrodite = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -0.1$, $r=1/10$.
%}
%\label{fig:LooseDecline}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%A neo-W can invade an XY system under a large number of selective regimes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\includegraphics[width=0.5\linewidth]{PositionPlot_4}
%\caption{
% A neo-W can invade an XY system under a large number of selective regimes.
%In panel A, there is no haploid selection ($t^\Hermaphrodite = \alpha^\Hermaphrodite_{\Delta} = 0$) and selection in diploids is sexually antagonistic ($s^\male = -s^\female = 1/10$, $h^\male = 1-h^\female = 3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$, gray region; but see Figure \ref{fig:SexAntagTighter}B for the case of very tight linkage).
%In panel B, male drive ($\alpha^\male_{\Delta} = -1/20$, $t^\Hermaphrodite = \alpha^\female_{\Delta} = 0$) opposes selection in diploids (no sex-differences: $s^\Hermaphrodite = 1/10$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can invade regardless of linkage.   
%In panel C, haploid competition in males ($t^\male = -1/10$, $t^\female = \alpha^\Hermaphrodite_{\Delta} = 0$) opposes selection in diploids (sex-differences: $s^\male = 3 s^\female = 3/20$, $h^\Hermaphrodite = 7/10$), in which case the neo-sex-determining allele can once again invade regardless of linkage.
%We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of recombination (an odd number of cross-over events).   
%}
%\label{fig:Combination_Centimorgans}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Sex-ratio selection is not a good predictor of neo-W invasion into an XY system
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\includegraphics[width=\linewidth]{Combination_Turnover_Ratio}
%\caption{
%Sex-ratio selection alone is not a good predictor of turnover between sex-determining systems.
%In panels A and C, male drive in an ancestral XY system causes a male bias, allowing a neo-W to invade and fix (causing the Y to fix in females), which balances the sex ratio (it also avoids selection in males, and thus makes better females in this case of sex-specific ploidally-antagonistic selection).
%In panels B and D, male drive in an ancestral ZW system has no affect on the sex ratio, yet a neo-Y can invade and fix (causing the W to fix in males) because it becomes linked with the driving allele, and this imparts a sex ratio bias.
%Parameters:  $s^\female =s^\male = 0.2$, $h^\female = h^\male = 0.7$, $t^\female = t^\male = \alpha^\male_\Delta = 0$, $\alpha^\female_\Delta = -1/10$, $r=1/20$.
%}
%\label{fig:SexRatioBad}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Haploid selection can lead to polymorphic SD systems 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\includegraphics[width=\linewidth]{Polymorphic}
%\caption{
%Tight linkage (relative to selection) and/or haploid selection can cause stable polymorphic sex-determining systems.
%In panel A, there is strong overdominance in both sexes and no haploid selection  (parameters as in Figure \ref{fig:BothOverdominance}B with $r = 1/10$), in which case a neo-W can invade regardless of sex-linkage, but cannot not fix (i.e., the Y does not fix in females, and X, Y, W, and Z all segregate at equilibrium).
%In panel B, there is sex-antagonistic selection at the diploid stage and drive in females (parameters as in Figure \ref{fig:SexAntagTighter} with $\alpha^\female_\Delta = 1/20$ and $r = 1/10$), in which case a sufficiently tightly linked neo-W can invade ($R<\sim r$), but only fixes if $R=0$.   
%}
%\label{fig:Polymorphism}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%CYCLES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[!h]
%\centering
%\includegraphics[width=0.5\linewidth]{BothWsInvade_Overdominance_Cycles}
%\caption{
%Thought I'd show this just for fun (not for publication).
%}
%\label{fig:Cycles}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage

@@

\section*{Supplementary Figures}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{PositionPlot_Overdominance_Mike}}
\caption{
Neo-W alleles can spread when loci under diploid selection are tightly linked to the ancestral sex determining locus ($r\approx0$). 
In panels A and B, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and selection in males is overdominant ($w_{aa}^\male=w_{AA}^\male=0.75$).
In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$). 
These parameters are marked by a dagger in Figure \ref{fig:regionplots}, which shows that neo-W invasion is expected for any $R$ when the $a$ allele is nearly fixed on the Y (black lines). 
Equilibria where the $A$ allele is more common among Y-bearing male gametes can also be stable for these parameters (blue lines). 
The weak selection approximation only holds when all recombination rates are large relative to selection (around 0 in panels A and C), in which case neo-W alleles should spread if they are more tightly linked to the selected locus (positive invasion fitness in the grey region). 
Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
}
\label{fig:positionOverdominance}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Temporal_Overdominance_Mike}}
\caption{
Following invasion by a neo-W allele, there can be a complete transition to a new sex-determination system, maintenance of polymorphism at both ancestral-XY and neo-ZW sex determining regions, or loss of the new sex-determining allele. 
Here we plot the frequency of the neo-W allele among female gametes; as the neo-W reaches frequency $0.5$, polymorphism at the ancestral XY locus is lost with Y becoming fixed such that sex is determined only be the ZW allele carried by a female gamete. 
Panels A, C and D show cases where a steady state is reached with the neo-W at a frequency below $0.5$, in which case ancestral-X and Y alleles also both segregate. 
In all cases, we assume that the $a$ allele is initially more common that the $A$ allele on the Y (Y$a$ is fixed when $r=0$). 
When $r>0$ (panels B and D), Y$A$ haplotypes created by recombination can become more common than Y$a$ haplotypes as the neo-W spreads.
In B, this leads to loss of the neo-W and the system goes to an equilibrium with X$a$ and Y$A$ haplotypes fixed (A'), such that all females have the high fitness genotype $aa$ and all males $Aa$. 
For the parameters in B, neo-W invasion fitness when the Y$A$ haplotype is ancestrally more common than Y$a$ (see blue line in Figure \ref{fig:temporalOverdominance}B). 
In contrast, the neo-W is not lost in panel D. 
Fitness parameters are the same as in Figure \ref{fig:temporalOverdominance}, the $a$ allele is favoured in females ($w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$) and there is overdominant selection in males ($w_{aa}^\male=w_{AA}^\male=0.75$) in panels A and B.
In panels C and D, selection in males and females is overdominant ($w_{aa}^\female=w_{AA}^\female=0.6$, $w_{aa}^\male=0.5$, $w_{AA}^\male=0.7$, $w_{Aa}^\Hermaphrodite=1$). 
These parameters are marked by a dagger in Figure \ref{fig:regionplots}. 
Here, there is no haploid selection $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$.
}
\label{fig:temporalOverdominance}
\end{figure}
